---
title: "Renthop Listing"
author: "Kanwal"
date: "4 March 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Renthop feature extraction

Browsing the data, I think the 'description', 'feature' and 'photo' columns should contain pretty valuable information, but they are a little bit hard to cope with. Here I tried to deal with 'feature' colums

Let's play with the renthop data.

## Load Data
```{r echo=TRUE, warning=FALSE, message = FALSE}
require(rjson)
require(dplyr)
require(purrr)
require(knitr)
require(stringr)

train = fromJSON(file = "C:/datasets/train.json")
test = fromJSON(file = "C:/datasets/test.json")

column <- setdiff(names(train), c("photos", "features"))
train <- map_at(train, column, unlist) %>% tibble::as_tibble(.)
# Number of listing in train set
#nrow(train)
test <- map_at(test, column, unlist) %>% tibble::as_tibble(.)
# Number of listing in test set
#nrow(test)
```

## Count Features

```{r eval = TRUE, echo=FALSE, message=FALSE}
# Total number of feature in train set
length(unique(train$features))
```

```{r eval = TRUE, echo=TRUE, message=FALSE}
# Summarize count of features
feature = data.frame(feature = tolower(unlist(train$features))) %>% # convert all features to lower case
  group_by(feature) %>%
  summarise(feature_count = n()) %>%
  arrange(desc(feature_count)) %>%
  filter(feature_count >= 50)

kable(feature, caption = "Feature Count")
```

We can easily observe from the table:-- 
- Among 10254 unique feature tags, most features are from top 10 features
- only 89 features show more than 50 times in train set.
- Among the list of top 89 features, many of them overlap each other.

## Synonmic features

```{r eval = TRUE, echo=TRUE, message=FALSE}
feature %>%
  filter(str_detect(feature, 'wood')) %>%
  kable(caption = "hardwood")


# Laundry in unit
feature %>%
  filter(str_detect(feature, paste(c('laundry', 'dryer', 'washer'), collapse="|"))) %>%
  filter(!str_detect(feature, "dishwasher")) %>%
  kable(caption = "Laundry in unit")

# Roof deck
feature %>%
  filter(str_detect(feature, 'roof')) %>%
  kable(caption = "Roof Deck")

# Outdoor space
feature %>%
  filter(str_detect(feature, 'outdoor')) %>%
  kable(caption = "Outdoor Space")

# Garden
feature %>%
  filter(str_detect(feature, 'garden')) %>%
  kable(caption = "Garden")

# Park
feature %>%
  filter(str_detect(feature, 'park')) %>%
  kable(caption = "Parking")
````

  
**Therefore, we can transform the features into categorial data, and reduce the number of categories by setting a cutoff count and combning features.**